EndoROAR Generator

### 2022-08-10 dev/notebooks/endo_roar_generator.qmd
all mitigation strategies somewhat effective

```{julia}
Λ₂ = [0.1, 1, 5]
counterfactuals_strict = []
generators = []
for λ₂ ∈ Λ₂  
    λ = [0.1, λ₂]
    generator = EndoROARGenerator(λ=λ)
    generators = vcat(generators..., generator)
    counterfactuals_strict = vcat(
      counterfactuals_strict...,
      generate_counterfactual(x, target, counterfactual_data, M, generator; convergence=:strict, T=T)
    )
end
```

@@

```{julia}
generators = Dict(
    :Generic => GenericGenerator(),
    :ROAR => EndoROARGenerator()
)
counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; convergence=:strict, T=T) for (name, gen) in generators])
```

>>>>

```{julia}
Λ₂ = [0.1, 1, 5]
counterfactuals_strict = []
generators = []
for λ₂ ∈ Λ₂  
    λ = [0.1, λ₂]
    generator = EndoROARGenerator(λ=λ)
    generators = vcat(generators..., generator)
    counterfactuals_strict = vcat(
      counterfactuals_strict...,
      generate_counterfactual(x, target, counterfactual_data, M, generator; T=T)
    )
end
```

@@

```{julia}
generators = Dict(
    :Generic => GenericGenerator(),
    :ROAR => EndoROARGenerator()
)
counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; T=T) for (name, gen) in generators])
```
